AIR4Children: Artificial Intelligence and Robotics for Children

### 2021-03-03 article/tex/main.tex

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
In this work, we proposed AIR4Children, artificial intelligence for children, as a way to (a) tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation and (b) to create affordable child-centred materials in AI and robotics.
We present current challenges and opportunities for a child-centred approaches for AI and robotics (AIR). 
Similarly, we touch on open-sourced software and hardware technologies to make a more inclusive, transparent and fair participation of children in areas of AIR. 
Then, we describe the avenues that AIR4Children can take with the development of open-sourced software and hardware.
Similarly, we propose to follow the philosophy of Montessori education 
to help children to not only develop computational thinking but also to internalise new concepts and learning skills through activities of movement and repetition with open source robots.
Finally, we add conclusions and mainly we pose the future work to go of AIR4children to putting in practice what is proposed here and measure the impact on AI and robotics of children. 
\end{abstract}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
We introduce AIR4Children, Artificial Intelligence for Children, as a way to (a) tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation and (b) to create affordable child-centred materials in AI and Robotics (AIR).
We present current challenges and opportunities for a child-centred approaches for AIR. 
Similarly, we touch on open-sourced software and hardware technologies to make a more inclusive, affordable and fair participation of children in areas of AIR. 
Then, we describe the avenues that AIR4Children can take with the development of open-sourced software and hardware.
Similarly, we propose to follow the philosophy of Montessori education to help children to not only develop computational thinking but also to internalise new concepts and learning skills through activities of movement and repetition with open source robots.
Finally, we conclude with few anecdotal experiences of our work and mainly we pose the future work of putting in practice what is proposed here to measure the impact on AIR in children of different socio-economical background, developmental stages and learning abilities. 
\end{abstract}
